---
title: "Blackpoll"
author: "Danni Harper"
date: "February 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loaded tidyverse
```{r}
library(tidyverse)
```

Read in data
```{r}
blackpoll <- read_rds("~/RMII/Blackpoll_Harper/blpw.all.RDS")
View(blackpoll)
```


Load date and time package
```{r}
library(lubridate)
```

Make date column
```{r}
blackpoll <- blackpoll %>%
  mutate(date = make_date(year, month, day))
```


Make date column with just month and day (for displaying all years together)
```{r}
blackpoll <- blackpoll %>%
  mutate(caught = make_date(!year, month, day))
```

See what columns are
```{r}
sapply(blackpoll, class)
```

Change date columns to integers to work with easier
```{r}
blackpoll$year<-as.integer(blackpoll$year)
blackpoll$month<-as.integer(blackpoll$month)
```

Organizing data my band number and date within band number. Then determine the change in mass from the capture, to the recapture events assuming that the first mass measurement was a capture (what if it wasn't??)
```{r}
bp.sorted <- blackpoll %>%
  group_by(band) %>%
  arrange(band,date) %>%
  mutate(diff_mass=mass-first(mass)) %>% 
  data.frame()
```

Get rid of non-recaptured birds
```{r}
bp.final <- filter(bp.sorted, recap == "R")
```

Graph
```{r}
ggplot(bp.final, aes(caught, diff_mass, colour = band, group = band))+
  geom_point()+
  geom_line()+
  xlab("Time of Year")+
  ylab("Mass (in grams, relative to capture date)")+
  facet_wrap(~location, nrow = 1)+
  theme(legend.position = 'none')
```


